Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-12 ms.tex
figures for cv3 tests.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{allamps.pdf}
\includegraphics[width=.49\columnwidth]{allamps_long_dark.pdf}
\caption{Reference pixel time series for a two frame integration (Left) and a long dark integration of 108 frames (Right). Each of the plots show that the pre-amplifier resets between frames in an integration cause discontinuities in the reference signal. Amplifiers 1 and 4 track the time all through a frame with the side reference pixels, whereas amplifiers 2 and 3 in the middle only contain information on the bottom and top reference pixels at the beginning and ending of a frame.
The long dark exposure example of 108 integrations shows the behavior over long timescales.}\label{fig:sampFig}
\end{figure}

@@

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy \\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{allamps.pdf}
\includegraphics[width=.49\columnwidth]{allamps_long_dark.pdf}
\caption{Reference pixel time series for a two frame integration (Left) and a long dark integration of 108 frames (Right). Each of the plots show that the pre-amplifier resets between frames in an integration cause discontinuities in the reference signal. Amplifiers 1 and 4 track the time all through a frame with the side reference pixels, whereas amplifiers 2 and 3 in the middle only contain information on the bottom and top reference pixels at the beginning and ending of a frame.
The long dark exposure example of 108 integrations shows the behavior over long timescales.}\label{fig:ampResetDark}
\end{figure}

@@

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy \\
OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging \\
GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
\end{deluxetable*}

\subsection{Cryogenic Vacuum (CV) Stability Tests}

Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images used the Crogenic Vacuum 3 (CV3) stability tests.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
\caption{Weak Lans +8 PSF during CV3 testing.
The central peak is used for centroiding the 70 pixel radius circular aperture.}\label{fig:WLP8PSF}
\end{figure}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
The WLP8SUB (subarray) showed the smallest standard deviation of any NIRCam mode explored.}\label{fig:CV3longTser}
\end{figure}
